\chapter{Results, Discussion and Conclusion}
\label{results}
\label{discussion}
In the beginning, i posed the question whether the information I gained during this short project might be insightful for customers and sellers. While it is certainly useful to have the data of two completely different sources combined and unified in one document, I was not able to do as much with the data as my initally intended to. It was possible to handle visualizing the data and applying KNN, but for more results (sales forecasts, most attractive location based on sales, etc.) the data was missing more columns such as actual sales data and reports. Nonetheless, I was able to apply many concepts I learned during the course and worked with my own goal in mind, always double checking with the labs from different weeks.

I was able to collect data from computer stores in my area using eBay and Foursquare. The results are somewhat insightful, as I could unify the two datasets and visualize the different locations and offerings within my area. One thing I noticed quite early when preprocessing the data is that some entries were mistakenly matched to a wrong state or even country, when geocoding the city names. While the coordinates could be easily identified and mapped to a town or city, the city name alone that was provided by eBay is not enough as there are multiple cities with the same name. However, these small outliers did not affect the result very much.

As for the conclusion of this project, I would like to say that I really enjoyed applying the concepts and methods that were presented in the course. The capstone project is more or less constructed and not really tied to a real world business case, but I still think that it acts great as a foundation for future work. The contents of the 9 courses do not cover everything I will ever come across in the field of data science, but I was able to gain a solid understanding of basic concepts and can make use of that in the future.